### 2018-07-05 paper/6-engineering.tex
Polish S6.3

\item[Volatility] Some tasks are defined to change in every execution, for
example \Excel provides a~``function'' \cmd{RANDBETWEEN} which produces a random
number in a specified range~--~on each recalculation it is defined to change.
Similarly, build systems like \Make and \Shake provide \emph{phony rules} which
are also volatile. The main difference from non-deterministic tasks, is that
volatile tasks cannot be cached. They are best handled by introducing a special
key \cmd{RealWorld} whose value is changed between every run.
\end{description}

@@

\noindent
Handling such tasks is possible in our framework, but requires an adjustment of
the correctness definition (\S\ref{sec-build-correctness}): instead of requiring
that the result of recomputing the \hs{task} matches the value stored in the
\hs{result}:
\[
\hs{getValue}~\hs{k}~\hs{result}~\hs{==}~\hs{compute}~\hs{task}~\hs{result}.
\]
\noindent
we now require that \hs{result} contains \emph{one possible result of recomputing}
the \hs{task}:
\[
\hs{getValue}~\hs{k}~\hs{result}~\hs{`elem`}~\hs{computeND}~\hs{task}~\hs{result}
\]
where
\hs{computeND}~\hs{::}~\hs{Task}~\hs{MonadPlus}~\hs{k}~\hs{v}~\hs{->}~\hs{Store}~\hs{i}~\hs{k}~\hs{v}~\hs{->}~\hs{[@@v]}
returns the list of all possible results of the \hs{task} instead of just one
value (`ND' stands for `non-deterministic').

>>>>

\item[Volatility] Some tasks are defined to change in every build, e.g. \Excel
provides a~``function'' \cmd{RANDBETWEEN} producing a fresh random number in a
specified range on each recalculation. Similarly, build systems like \Make and
\Shake provide volatile \emph{phony rules}. The main difference from
non-deterministic tasks is that volatile tasks cannot be cached. They are best
modelled as depending on a special key \cmd{RealWorld} whose value is changed
in every build.
\end{description}

@@

\noindent
Such tasks can be modelled in our framework by adjusting the correctness
definition (\S\ref{sec-build-correctness}): instead of requiring that the
\hs{result}ing value \emph{equals} the one obtained by recomputing the \hs{task}:
\[
\hs{getValue}~\hs{k}~\hs{result}~\hs{==}~\hs{compute}~\hs{task}~\hs{result}\text{,}
\]
\noindent
we now require that \hs{result} contains \emph{one possible result of
recomputing} the \hs{task}:
\[
\hs{getValue}~\hs{k}~\hs{result}~\hs{`elem`}~\hs{computeND}~\hs{task}~\hs{result}\text{,}
\]
where
\hs{computeND}~\hs{::}~\hs{Task}~\hs{MonadPlus}~\hs{k}~\hs{v}~\hs{->}~\hs{Store}~\hs{i}~\hs{k}~\hs{v}~\hs{->}~\hs{[@@v]}
returns the list of all possible results of the \hs{task} instead of just one
value (`ND' stands for `non-deterministic').
